---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup}
library(tidyverse)
```

# Importing data

```{r}
download.file('http://www.equality-of-opportunity.org/data/college/mrc_table1.xlsx', 
              destfile = 'mrc_table1.xlsx',
              method='curl')
ratings <- readxl::read_excel('mrc_table1.xlsx')
```

But the column names are not useful:

```{r}
ratings %>% colnames
```

So we specify the names of columns (skipping first row since it is the header):

```{r}
ratings <- readxl::read_excel('mrc_table1.xlsx',
                              skip = 1,
                              col_names = c('ipedid', 
                                            'institution', 
                                            'metroarea', 
                                            'state', 
                                            'median_parent_hhold_income', 
                                            'median_child_indiv_earnings', 
                                            'low_income_access', 
                                            'percent_parents_in_top1percent', 
                                            'success_rate', 
                                            'uppertail_success_rate', 
                                            'mobility_rate', 
                                            'uppertail_mobility_rate', 
                                            'change_percent_parents_bottom_quintile', 
                                            'change_percent_parents_bottom_40', 
                                            'number_students_cohort'))
```

# Exploring CUNY

Unfortunately, there is no yes/no column that tells us if a school is in CUNY or not. 

Let's start by a simple filter then. We will use the 

```{r}
ratings %>%
  filter(stringr::str_detect(institution, 'Baruch'))
```

So maybe the way to get the CUNY schools is to filter for "CUNY"! Let's give that a try:

```{r}
ratings %>%
  filter(stringr::str_detect(stringr::str_to_upper(institution), 'CUNY'))
```

There are more than 16 schools in CUNY but this will work for now.

Let's order CUNY schools by their mobility ratings:

```{r}
ratings %>%
  filter(stringr::str_detect(stringr::str_to_upper(institution), 'CUNY')) %>% 
  select(institution, mobility_rate)
  arrange(-mobility_rate)
```

# Visualizing the data

Let's begin by summarizing the distribution of the mobility rates.

```{r}
ratings %>% 
  ggplot(aes(x=mobility_rate)) + 
    geom_histogram(aes(y=..density..), 
                   binwidth=.1,
                   color="black",
                   fill="white") +
    geom_vline(aes(xintercept=mean(mobility_rate, na.rm=T)),   # Ignore NA values for mean
               color="red", linetype="dashed", size=1) +
    geom_density(alpha=.2, fill="#FF6666")
```

So what were the schools that were in the top 50 of ratings?

```{r fig.width=10,fig.height=10}
library(forcats)
ratings %>% 
  arrange(-mobility_rate) %>%
  select(institution, mobility_rate) %>%
  head(50) %>%
  ggplot(aes(fct_reorder(as.factor(institution), mobility_rate), mobility_rate)) + 
    geom_bar(stat='identity') + 
    labs(title="Mobility rate of top colleges") +
    xlab('') +
    ylab('') +
    geom_text(aes(label=sprintf('%0.2f', mobility_rate)), 
              hjust=1.5,
              vjust=0.25,
              size=2.5,
              position = position_dodge(width = 1), 
              colour="white",
              fontface = "bold",
              inherit.aes = TRUE) +
    coord_flip()
```

# Models

```{r}
ratings %>%
  ggplot(aes(percent_parents_in_top1percent, success_rate)) +
    geom_point()
```

```{r}
lmfit <- lm(success_rate ~ percent_parents_in_top1percent, data = ratings)
```

We can use the standard base `summary()` to inspect the fitted model:

```{r}
summary(lmfit)
```

But we can avoid the headaches of the R built-in classes by using the `broom` package from the tidyverse:

```{r}
broom::tidy(lmfit)
broom::glance(lmfit)
```