---
title: "Data Exercise"
---

```{r setup}
library(tidyverse)
```

# Importing data

```{r}
url <- 'http://www.equality-of-opportunity.org/data/college/mrc_table1.csv'
ratings <- readr::read_csv(url)
```

But the column names are not useful:

```{r}
ratings %>% colnames
```

# Exploring CUNY

Unfortunately, there is no yes/no column that tells us if a school is in CUNY or not. 

Let's start by a simple filter then. We will use the 

```{r}
ratings %>%
  filter(stringr::str_detect(name, 'Baruch'))
```

So maybe the way to get the CUNY schools is to filter for "CUNY"! Let's give that a try:

```{r}
ratings %>%
  filter(stringr::str_detect(stringr::str_to_upper(name), 'CUNY'))
```

There are more than 16 schools in CUNY but this will work for now.

Let's order CUNY schools by their mobility ratings, highest to lowest:

```{r}
ratings %>%
  filter(stringr::str_detect(stringr::str_to_upper(name), 'CUNY')) %>% 
  select(name, mr_kq5_pq1) %>%
  arrange(-mr_kq5_pq1) %>%
  head(10)
```

# Visualizing the data

Let's begin by summarizing the distribution of the mobility rates.

```{r}
ratings %>% 
  ggplot(aes(x=mr_kq5_pq1)) + 
    geom_histogram(aes(y=..density..), 
                   binwidth=.1,
                   color="black",
                   fill="white") +
    geom_vline(aes(xintercept=mean(mr_kq5_pq1, na.rm=T)),   # Ignore NA values for mean
               color="red", linetype="dashed", size=1) +
    geom_density(alpha=.2, fill="#FF6666")
```

So what were the schools that were in the top 50 of ratings?

```{r fig.width=10,fig.height=10}
library(forcats)
ratings %>% 
  arrange(-mr_kq5_pq1) %>%
  select(name, mr_kq5_pq1) %>%
  head(50) %>%
  ggplot(aes(fct_reorder(as.factor(name), mr_kq5_pq1), mr_kq5_pq1)) + 
    geom_bar(stat='identity') + 
    labs(title="Mobility rate of top colleges") +
    xlab('') +
    ylab('') +
    geom_text(aes(label=sprintf('%0.2f', mr_kq5_pq1)), 
              hjust=1.5,
              vjust=0.25,
              size=2.5,
              position = position_dodge(width = 1), 
              colour="white",
              fontface = "bold",
              inherit.aes = TRUE) +
    coord_flip()
```
